---
title: "p8105_hw3_yx2710"
output: github_document
---

```{r setup}
library(tidyverse)
library(p8105.datasets)
```

Problem 1 

```{r} 
data("instacart")
```

Short description of the instacart dataset:
The instacart dataset has `r nrow(instacart)` rows and `r ncol(instacart)` columns. The variables that the instacart dataset contain are `r names(instacart)`

* "reordered": 1 means this product has been ordered by this user before, 0 otherwise.

* "eval_set":  which evaluation set this order is included (Note that eval_set of this dataset is exclusively from the “train”)

* "order_dow": the day of the week on which the order was placed

* "aisle": the name of the aisle

* "department": the name of the department

Q:How many aisles are there, and which aisles are the most items ordered from?
```{r}
instacart %>% 
  count(aisle, name = "n") %>% 
  arrange(-n)
```
A: There are 134 aisles and fresh vegetables are the most items ordered from.

Q: Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>% 
  count(aisle, name = "n") %>%
  filter(n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n, .desc = TRUE)) %>% 
  ggplot(aes(x = aisle, y = n)) + geom_point() +
  labs(
    title = "Number of items ordered in each aisle",
    x = "Aisle",
    y = "Number of items ordered",
    caption = "Oder number larger than 10,000"
  )+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
A: The plot is shown here and this plot also shows the answer that fresh vegetables are the most items ordered from.

Q:Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
instacart %>% 
  filter(aisle == c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(count = n()) %>% 
  top_n(3, count) %>% 
  knitr::kable()
```

A: The table is shown here.

Q: Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = product_name,
    values_from = mean_hour
  ) %>% 
  knitr::kable()
```
A: The table is shown here.








